---
title: "Visualisation of data on cross-regional Electoral Malpractice in Russia"
author: "ElMaRB project"
date: "1/23/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#knitr::opts_chunk$set(fig.width=14, fig.height=10)
```




```{r, results='hide', error=FALSE, warning=FALSE,echo=FALSE,message=FALSE}
setwd("/Users/valeriacaras/Downloads/R Studio")
library(readxl)
library(dplyr)
library(ggplot2)
library(readxl)
library(reshape2)
library(plotly)
library(tidyr)
library(ggrepel)
data_RUregions <- read_excel("data_RUregions_112021.xlsx")
#summary(data_RUregions)



```

### Overall number of messages on electoral fraud for all elections in the dataset
```{r,error=FALSE, warning=FALSE, echo=FALSE, fig.width=36, fig.height=8}
#cumm_data <-  data_RUregions %>% summarise(sum_all_mess2021 = sum(elect_mess_parl_2021, na.rm = T), sum_fals_mess2021 = sum(mess_fals_parl_2021, na.rm = T),sum_fals_mess2016 = sum(mess_fals_parl_2016,na.rm = T), sum_all_mess2016 = sum(elect_mess_parl_2016,na.rm = T), sum_fals_mess2016 = sum(mess_fals_parl_2016,na.rm = T),sum_all_mess2011 = sum(elect_mess_parl2011,na.rm = T), sum_fals_mess2011 = sum(mess_fals_parl_2011,na.rm = T),sum_all_mess2007 = sum(elect_mess_parl2007,na.rm = T), sum_fals_mess2007 = sum(mess_fals_parl_2007,na.rm = T),sum_all_mess2018 = sum(elect_mess_pres2018,na.rm = T), sum_fals_mess2018 = sum(mess_fals_presid_2018,na.rm = T),sum_all_mess2012 = sum(elect_mess_pres2012,na.rm = T), sum_fals_mess2012 = sum(mess_fals_presid_2012,na.rm = T),sum_all_mess2008 = sum(elect_mess_pres2008,na.rm = T), sum_fals_mess2008 = sum(mess_fals_presid_2008,na.rm = T))
  


#cumm_data1 <- cumm_data %>% gather(1:14, key = "variable",value="value") %>% arrange(variable)

#cumm_data1['elections'] <- c("State Duma 2007","Presidential 2008","State Duma 2011","Presidential 2012","State Duma 2016","Presidential 2018","State Duma 2021","State Duma 2007","Presidential 2008","State Duma 2011","Presidential 2012","State Duma 2016","Presidential 2018","State Duma 2021")

#cumm_data1$variable <- as.character(cumm_data1$variable )

#write.csv(cumm_data1, 'cumm_data1.csv')

cumm_data_all <- read_excel("cumm_data.xlsx", 
    col_types = c("text", "numeric", "text","numeric"))

cumm_messages <- cumm_data_all  %>% 
  ggplot(., aes(y = value, x = elections,  fill = variable)) + geom_col() + geom_text(aes(label = value), size = 8, vjust = 0.8) + 
  theme_minimal() + 
  labs(y = "Number of messages in regional media") + theme(legend.title  = element_blank(), legend.text = element_text(size=26),axis.text.x = element_text(size = 30), axis.title.x  = element_blank(),axis.title.y  = element_text(size = 30), axis.text.y = element_text(size=26)) + 
  scale_x_discrete(limits = c("State Duma 2007", "Presidential 2008","State Duma 2011","Presidential 2012","State Duma 2016",
                              "Presidential 2018","State Duma 2021"))
  
cumm_messages 
```

### Percentage of messages on electoral fraud for all elections in the dataset
```{r,error=FALSE, warning=FALSE, echo=FALSE, fig.width=36, fig.height=8}

cumm_messages_perc <- cumm_data_all%>% 
  ggplot(., aes(y = perc_fals, x = elections)) + geom_col(fill = "indianred2") + 
  theme_minimal() + 
  labs(y = "% of fraud messages in regional media") + theme(legend.title  = element_blank(), legend.text = element_text(size=26),axis.text.x = element_text(size = 30), axis.title.x  = element_blank(),axis.title.y  = element_text(size = 30),axis.text.y = element_text(size=26)) + 
  scale_x_discrete(limits = c("State Duma 2007", "Presidential 2008","State Duma 2011","Presidential 2012","State Duma 2016",
                              "Presidential 2018","State Duma 2021")) 
  
cumm_messages_perc 

```



### Average number of messages on electoral fraud for all elections in the dataset
```{r,error=FALSE, warning=FALSE, echo=FALSE, fig.width=36, fig.height=8}


avgdata <- read_excel("avg_data.xlsx")
#install.packages("reshape2")

avgdata2 <- melt(avgdata, id.vars='elections')

#average_messages_per_election <- avgdata2 %>% ggplot(., aes(y = value, x = elections, fill = variable)) + geom_bar(stat='identity', position='dodge') + geom_text(aes(label = value), size = 3, vjust = 1.5, position = position_dodge(.9))
#average_messages_per_election


average_messages_per_election1 <- avgdata2 %>% 
  ggplot(., aes(y = value, x = elections,  fill = variable)) + geom_col() + geom_text(aes(label = value), size = 8, vjust = 0.8) + 
  theme_minimal() + 
  labs(y = "Number of messages in regional media") + theme(legend.title  = element_blank(), legend.text = element_text(size=26),axis.text.x = element_text(size = 30), axis.title.x  = element_blank(),axis.title.y  = element_text(size = 30), axis.text.y = element_text(size=26)) + 
  scale_fill_discrete(labels =  c("Average number of messages on elections", "Average number of messages on electoral fraud")) +
  scale_x_discrete(limits = c("State Duma 2007", "Presidential 2008","State Duma 2011","Presidential 2012","State Duma 2016",
                              "Presidential 2018","State Duma 2021"))
  
average_messages_per_election1


```

```{r,error=FALSE, warning=FALSE, echo=FALSE, fig.width=36, fig.height=8}


average_messages_per_election2 <- avgdata2 %>% 
  ggplot(., aes(y = value, x = elections,  fill = variable)) + geom_col(position = "fill") + 
  theme_minimal() + 
  labs(y = "Messages in regional media") + theme(legend.title  = element_blank(), legend.text = element_text(size=26),axis.text.x = element_text(size = 30), axis.title.x  = element_blank(),axis.title.y  = element_text(size = 30),axis.text.y = element_text(size=26)) + 
  scale_fill_discrete(labels =  c("Messages on elections", "% messages on electoral fraud")) +
  scale_x_discrete(limits = c("State Duma 2007", "Presidential 2008","State Duma 2011","Presidential 2012","State Duma 2016",
                              "Presidential 2018","State Duma 2021")) +   scale_y_continuous(labels = scales::percent)
  
average_messages_per_election2

```



## Share of messages on electoral fraud from the total amount of messages {.tabset .tabset-pills}

### State Duma elections 2007
```{r,error=FALSE, warning=FALSE, fig.align='left',echo=FALSE,fig.width=12, fig.height=10}

share_regions2007 <- data_RUregions %>% filter(per_violmess_all_parl07 > 0) %>%
  ggplot(., aes(y = reorder(r_name, per_violmess_all_parl07), x = per_violmess_all_parl07)) + geom_col(position = "dodge", colour = "black", fill = "indianred2") + theme_minimal() + labs(x = "share by region") + theme(axis.title.y = element_blank())
#share_regions2007

share_regions2007_plotly <-ggplotly(share_regions2007, tooltip = c("x"))
share_regions2007_plotly
```

### Presidential elections 2008
```{r,error=FALSE, warning=FALSE, fig.align='left',echo=FALSE,fig.width=12, fig.height=10}
share_regions_presid2008  <- data_RUregions %>% filter(per_violmess_all_pres08 > 0) %>%
  ggplot(., aes(y = reorder(r_name, per_violmess_all_pres08), x = per_violmess_all_pres08)) + geom_col(position = "dodge", colour = "black", fill = "indianred2") + theme_minimal() + labs(x = "share by region") + theme(axis.title.y = element_blank())
#share_regions_presid2012

share_regions_presid2008_plotly <-ggplotly(share_regions_presid2008, tooltip = c("x"))
share_regions_presid2008_plotly
```

### State Duma elections 2011
```{r,error=FALSE, warning=FALSE, fig.align='left',echo=FALSE,fig.width=12, fig.height=10}
share_regions2011 <- data_RUregions %>% filter(per_violmess_all_parl11 > 0) %>%
  ggplot(., aes(y = reorder(r_name, per_violmess_all_parl11), x = per_violmess_all_parl11)) + geom_col(position = "dodge", colour = "black", fill = "indianred2") + theme_minimal() + labs(x = "share by region") + theme(axis.title.y = element_blank())
#share_regions2011

share_regions2011_plotly <-ggplotly(share_regions2011, tooltip = c("x"))
share_regions2011_plotly
```


### Presidential elections 2012
```{r,error=FALSE, warning=FALSE, fig.align='left',echo=FALSE,fig.width=12, fig.height=10}
share_regions_presid2012  <- data_RUregions %>% filter(per_violmess_all_pres12 > 0) %>%
  ggplot(., aes(y = reorder(r_name, per_violmess_all_pres12), x = per_violmess_all_pres12)) + geom_col(position = "dodge", colour = "black", fill = "indianred2") + theme_minimal() + labs(x = "share by region") + theme(axis.title.y = element_blank())
#share_regions_presid2012

share_regions_presid2012_plotly <-ggplotly(share_regions_presid2012, tooltip = c("x"))
share_regions_presid2012_plotly
```


### State Duma elections 2016
```{r,error=FALSE, warning=FALSE, fig.align='left',echo=FALSE,fig.width=12, fig.height=10}
share_regions2016 <- data_RUregions %>% filter(per_violmess_all_parl16 > 0) %>%
  ggplot(., aes(y = reorder(r_name, per_violmess_all_parl16), x = per_violmess_all_parl16)) + geom_col(position = "dodge", colour = "black", fill = "indianred2") + theme_minimal() + labs(x = "share by region") + theme(axis.title.y = element_blank())
#share_regions2016

share_regions2016_plotly <-ggplotly(share_regions2016, tooltip = c("x"))
share_regions2016_plotly
```

### Presidential elections 2018
```{r,error=FALSE, warning=FALSE, fig.align='left',echo=FALSE,fig.width=12, fig.height=10}
share_regions_presid2018 <- data_RUregions %>% filter(per_violmess_all_pres18 > 0) %>%
  ggplot(., aes(y = reorder(r_name, per_violmess_all_pres18), x = per_violmess_all_pres18)) + geom_col(position = "dodge", colour = "black", fill = "indianred2") + theme_minimal() + labs(x = "share by region") + theme(axis.title.y = element_blank())
#share_regions_presid2018 

share_regions_presid2018_plotly <-ggplotly(share_regions_presid2018, tooltip = c("x"))
share_regions_presid2018_plotly
```

### State Duma elections 2021

```{r,error=FALSE, warning=FALSE, echo=FALSE,fig.align='left',fig.width=12, fig.height=10}

data_RUregions$per_violmess_all_parl21 <- round(data_RUregions$per_violmess_all_parl21, digits = 2)

share_regions2021 <- data_RUregions %>% filter(per_violmess_all_parl21 > 0) %>%
  ggplot(., aes(y = reorder(r_name, per_violmess_all_parl21), x = per_violmess_all_parl21)) + 
  geom_col(position = "dodge", colour = "black", fill = "indianred2") + theme_minimal() + 
  labs(x = "% of messages on electoral fraud from the total amount of messages") + 
  theme(axis.title.y = element_blank())
#share_regions2021

share_regions2021_plotly <-ggplotly(share_regions2021, tooltip = c("x"))
share_regions2021_plotly

#Sys.setenv("plotly_username"=  "valeria_caras")
#Sys.setenv("plotly_api_key"=  "5RQXXYgmgwxRPPcCwr2M")
#api_create(share_regions2021_plotly, filename ="share_regions2021_plotly")
```




## {-}



## Total number of messages on elections and violations by region  {.tabset .tabset-pills}

### State Duma elections 2007
```{r,error=FALSE, warning=FALSE,fig.align='left', echo=FALSE,fig.width=12, fig.height=10}

data07elections <- data_RUregions %>% select(r_name, elect_mess_parl2007, mess_fals_parl_2007)
data07elections2 <- melt(data07elections, id.vars='r_name')
data07elections2$variable <- as.character(data07elections2$variable)
data07elections2$variable[data07elections2$variable == 'elect_mess_parl2007'] <- 'Number of messages on elections'
data07elections2$variable[data07elections2$variable == 'mess_fals_parl_2007'] <- 'Number of messages on electoral fraud'

messages_per_2007election <- data07elections2 %>% filter(r_name != "Moskva" & value > 0) %>% 
  ggplot(., aes(y = value, x = reorder(r_name, value), fill = variable)) + geom_col() + theme_minimal() + labs(y = "Number of messages in regional media: State Duma elections 2007") + theme(legend.title  = element_blank(), axis.title.y = element_blank()) +  coord_flip()
#messages_per_2007election

ggplotly(messages_per_2007election, tooltip = c("y"))  

```

### Presidential elections 2008
```{r,error=FALSE, warning=FALSE,fig.align='left',echo=FALSE,fig.width=12, fig.height=10}

data08elections <- data_RUregions %>% select(r_name, elect_mess_pres2008, mess_fals_presid_2008)
data08elections2 <- melt(data08elections, id.vars='r_name')
data08elections2$variable <- as.character(data08elections2$variable)
data08elections2$variable[data08elections2$variable == 'elect_mess_pres2008'] <- 'Number of messages on elections'
data08elections2$variable[data08elections2$variable == 'mess_fals_presid_2008'] <- 'Number of messages on electoral fraud'

messages_per_2008_preselection <- data08elections2 %>% filter(r_name != "Moskva" & value > 0) %>% 
  ggplot(., aes(y = value, x = reorder(r_name, value), fill = variable)) + geom_col() + theme_minimal() + labs(y = "Number of messages in regional media: Presidential elections 2012") + theme(legend.title  = element_blank(), axis.title.y = element_blank()) + coord_flip()
#messages_per_2008_preselection

messages_per_2008_preselection_plotly <-ggplotly(messages_per_2008_preselection, tooltip = c("y"))
messages_per_2008_preselection_plotly
```

### State Duma elections 2011
```{r,error=FALSE, warning=FALSE,fig.align='left', echo=FALSE,fig.width=12, fig.height=10}

data11elections <- data_RUregions %>% select(r_name, elect_mess_parl2011, mess_fals_parl_2011)
data11elections2 <- melt(data11elections, id.vars='r_name')
data11elections2$variable <- as.character(data11elections2$variable)
data11elections2$variable[data11elections2$variable == 'elect_mess_parl2011'] <- 'Number of messages on elections'
data11elections2$variable[data11elections2$variable == 'mess_fals_parl_2011'] <- 'Number of messages on electoral fraud'

messages_per_2011election <- data11elections2 %>% filter(r_name != "Moskva" & value > 0) %>% 
  ggplot(., aes(y = value, x = reorder(r_name, value), fill = variable)) + geom_col() + theme_minimal() + labs(y = "Number of messages in regional media: State Duma elections 2011") + theme(legend.title  = element_blank(), axis.title.y = element_blank()) + coord_flip()
#messages_per_2011election

messages_per_2011election_plotly <-ggplotly(messages_per_2011election, tooltip = c("y"))
messages_per_2011election_plotly
```


### Presidential elections 2012
```{r,error=FALSE, warning=FALSE,fig.align='left',echo=FALSE,fig.width=12, fig.height=10}

data12elections <- data_RUregions %>% select(r_name, elect_mess_pres2012, mess_fals_presid_2012)
data12elections2 <- melt(data12elections, id.vars='r_name')
data12elections2$variable <- as.character(data12elections2$variable)
data12elections2$variable[data12elections2$variable == 'elect_mess_pres2012'] <- 'Number of messages on elections'
data12elections2$variable[data12elections2$variable == 'mess_fals_presid_2012'] <- 'Number of messages on electoral fraud'

messages_per_2012_preselection <- data12elections2 %>% filter(r_name != "Moskva" & value > 0) %>% 
  ggplot(., aes(y = value, x = reorder(r_name, value), fill = variable)) + geom_col() + theme_minimal() + labs(y = "Number of messages in regional media: Presidential elections 2012") + theme(legend.title  = element_blank(), axis.title.y = element_blank()) +  coord_flip()
#messages_per_2012_preselection

messages_per_2012_preselection_plotly <-ggplotly(messages_per_2012_preselection, tooltip = c("y"))
messages_per_2012_preselection_plotly
```

### State Duma elections 2016
``` {r,error=FALSE, warning=FALSE, echo=FALSE,message=FALSE,fig.width=12, fig.height=10}
data16elections <- data_RUregions %>% select(r_name, elect_mess_parl2016, mess_fals_parl_2016)
data16elections2 <- melt(data16elections, id.vars='r_name')
data16elections2$variable <- as.character(data16elections2$variable)
data16elections2$variable[data16elections2$variable == 'elect_mess_parl2016'] <- 'Number of messages on elections'
data16elections2$variable[data16elections2$variable == 'mess_fals_parl_2016'] <- 'Number of messages on electoral fraud'

messages_per_2016election <- data16elections2 %>% filter(r_name != "Moskva" & value > 0) %>% 
  ggplot(., aes(y = value, x = reorder(r_name, value), fill = variable)) + geom_col() + theme_minimal() + labs(y = "Number of messages in regional media: State Duma elections 2016") + theme(legend.title  = element_blank(), axis.title.y = element_blank()) +  coord_flip()
#messages_per_2016election


messages_per_2016election_plotly <-ggplotly(messages_per_2016election, tooltip = c("y"))
messages_per_2016election_plotly
```



### Presidential elections 2018
```{r,error=FALSE, warning=FALSE,fig.align='left', echo=FALSE,fig.width=12, fig.height=10}

data18elections <- data_RUregions %>% select(r_name, elect_mess_pres2018, mess_fals_presid_2018)
data18elections2 <- melt(data18elections, id.vars='r_name')
data18elections2$variable <- as.character(data18elections2$variable)
data18elections2$variable[data18elections2$variable == 'elect_mess_pres2018'] <- 'Number of messages on elections'
data18elections2$variable[data18elections2$variable == 'mess_fals_presid_2018'] <- 'Number of messages on electoral fraud'

messages_per_2018_preselection <- data18elections2 %>% filter(r_name != "Moskva" & value > 0) %>% 
  ggplot(., aes(y = value, x = reorder(r_name, value), fill = variable)) + geom_col() + theme_minimal() + labs(y = "Number of messages in regional media: Presidential elections 2018") + theme(legend.title  = element_blank(), axis.title.y = element_blank()) + coord_flip()
#messages_per_2018_preselection

messages_per_2018_preselection_plotly <-ggplotly(messages_per_2018_preselection, tooltip = c("y"))
messages_per_2018_preselection_plotly
```

### State Duma elections 2021

```{r,error=FALSE, warning=FALSE,fig.align='left', echo=FALSE,fig.width=12, fig.height=10}

data21elections <- data_RUregions %>% select(r_name, elect_mess_parl_2021, mess_fals_parl_2021)
data21elections2 <- melt(data21elections, id.vars='r_name')
data21elections2$variable <- as.character(data21elections2$variable)
data21elections2$variable[data21elections2$variable == 'elect_mess_parl_2021'] <- 'Number of messages on elections'
data21elections2$variable[data21elections2$variable == 'mess_fals_parl_2021'] <- 'Number of messages on electoral fraud'

messages_per_2021election <- data21elections2 %>% filter(r_name != "Moskva" & value > 0) %>% 
  ggplot(., aes(y = value, x = reorder(r_name, value), fill = variable)) + geom_col() + theme_minimal() + labs(y = "number of messages") + theme(legend.title  = element_blank(), axis.title.y = element_blank()) +  coord_flip()
#messages_per_2021election

messages_per_2021election_plotly <-ggplotly(messages_per_2021election, tooltip = c("y")) 
messages_per_2021election_plotly

#Sys.setenv("plotly_username"=  "valeria_caras")
#Sys.setenv("plotly_api_key"=  "5RQXXYgmgwxRPPcCwr2M")
#api_create(messages_per_2021election_plotly, filename ="messages_per_2021election_plotly")
```



## {-}

## Total number of messages on elections and violations for Mosсow city as an outlier  

```{r,error=FALSE, warning=FALSE,fig.align='left', echo=FALSE,fig.width=12, fig.height=4}

#data_moskow <- data_RUregions %>% filter(r_name == "Moskva") %>% select(r_name, elect_mess_parl2007, mess_fals_parl_2007,elect_mess_pres2008, mess_fals_presid_2008,elect_mess_parl2011, mess_fals_parl_2011,elect_mess_pres2012, mess_fals_presid_2012,elect_mess_parl2016, mess_fals_parl_2016,elect_mess_pres2018, mess_fals_presid_2018,elect_mess_parl_2021, mess_fals_parl_2021)


#data_moskow1 <- data_moskow %>% gather(2:15, key = "variable",value="value") %>% arrange(variable)


#write.csv(data_moskow1, 'data_moskow1.csv')

data_moscow <- read_excel("data_moscow.xlsx", col_types = c("text", "text", "numeric", "text"))

moscow_plot<- data_moscow  %>% 
  ggplot(., aes(y = value, x = elections, fill = variable)) + geom_col() + theme_minimal() + labs(y = "Number of messages in Moscow media")  + theme(legend.title  = element_blank(), axis.title.x  = element_blank()) + 
  scale_x_discrete(limits = c("State Duma 2007", "Presidential 2008","State Duma 2011","Presidential 2012","State Duma 2016",
                              "Presidential 2018","State Duma 2021"))

#moscow_plot

ggplotly(moscow_plot)
```




## Gross regional product and share of messages on electoral fraud  {.tabset .tabset-pills}

### State Duma elections 2011
```{r,error=FALSE, warning=FALSE,fig.align='left', echo=FALSE,message=FALSE,fig.width=8, fig.height=6}

grp_elections2011 <-ggplot(data_RUregions, aes(x = per_violmess_all_parl11, y = log(grp_capita2011))) + geom_point(aes(label = r_name),colour = "indianred2", size = 3) + theme_minimal()+ labs(y = "Gross regional product in 2011", x = "% electoral violations in State  Duma elections 2011") +  geom_smooth(method='loess') 
#grp_elections2011

ggplotly(grp_elections2011)
```

### Presidential elections 2012
```{r,error=FALSE, warning=FALSE,fig.align='left',echo=FALSE,message=FALSE,fig.width=8, fig.height=6}
grp_elections2012 <-ggplot(data_RUregions, aes(x = per_violmess_all_pres12, y = log(grp_capita2012))) +
  geom_point(aes(label =  r_name), colour = "indianred2", size = 3) + theme_minimal() + labs(y = "Gross regional product in 2012", x = "% messages on electoral violations in Presendiatial elections 2012") + geom_smooth(method='loess') 
#grp_elections2012

ggplotly(grp_elections2012)
```

### State Duma elections 2016

```{r,error=FALSE, warning=FALSE,fig.align='left', echo=FALSE,message=FALSE,fig.width=8, fig.height=6}
grp_elections2016 <-ggplot(data_RUregions, aes(x = per_violmess_all_parl16, y = log(grp_capita2016))) + geom_point(aes(label = r_name),colour = "indianred2", size = 3) + theme_minimal()+ labs(y = "Gross regional product in 2016", x = "% electoral violations in State  Duma elections 2016") +  geom_smooth(method='loess') 
#grp_elections2016

ggplotly(grp_elections2016)
```

### Presidential elections 2018
```{r,error=FALSE, warning=FALSE,fig.align='left',echo=FALSE,message=FALSE,fig.width=8, fig.height=6}
grp_elections2018 <-ggplot(data_RUregions, aes(x = per_violmess_all_pres18, y = log(grp_capita2018))) +
  geom_point(aes(label =  r_name), colour = "indianred2", size = 3) + theme_minimal() + labs(y = "Gross regional product in 2018", x = "% messages on electoral violations in Presendiatial elections 2018") + geom_smooth(method='loess') 
#grp_elections2018

ggplotly(grp_elections2018)
```

### State Duma elections 2021
```{r,error=FALSE, warning=FALSE,fig.align='left', echo=FALSE,message=FALSE,fig.width=8, fig.height=6}
## выборы 2021 и ВРП за 2018 год (последнее подступное измерение)
grp_elections2021 <-ggplot(data_RUregions, aes(x = per_violmess_all_parl21, y = log(grp_capita2018))) +
  geom_point(aes(label =  r_name), colour = "indianred2", size = 3) + theme_minimal() + labs(y = "Gross regional product in 2018", x = " % messages on electoral violations in State Dumaelections 2021") +  geom_smooth(method='loess') 
#grp_elections2021

ggplotly(grp_elections2021)

#Sys.setenv("plotly_username"=  "valeria_caras")
#Sys.setenv("plotly_api_key"=  "5RQXXYgmgwxRPPcCwr2M")
#api_create(grp_elections2021, filename ="grp_elections2021")
```

## {-}




## Turnout and messages  on electoral fraud  {.tabset .tabset-pills}


### State Duma elections 2007
```{r, error=FALSE, warning=FALSE,fig.align='left',echo = FALSE,message=FALSE,fig.width=8, fig.height=6}
turnout_mess_2007 <-ggplot(data_RUregions, aes(x = per_violmess_all_parl07, y = log(turnout_gd2007))) +
  geom_point(aes(label =  r_name),colour = "indianred2", size = 3) + theme_minimal() +  labs(y = "Turnout %", x = "% messages on electoral violations in State Duma elections 2007") + geom_smooth(method="loess") 
#turnout_mess_2011

ggplotly(turnout_mess_2007)
```


### Presidential elections 2008
```{r, error=FALSE, warning=FALSE,fig.align='left',echo = FALSE, message=FALSE,fig.width=8, fig.height=6}

turnout_mess_2008 <-ggplot(data_RUregions, aes(x = per_violmess_all_pres08, y = log(turnout_presd_08))) +
  geom_point(aes(label =  r_name),colour = "indianred2", size = 3) + theme_minimal() +  labs(y = "Turnout %", x = "% messages on electoral violations in Presidential elections 2008") + geom_smooth(method = "lm") 
#turnout_mess_2008
ggplotly(turnout_mess_2008)
```

### State Duma elections 2011
```{r, error=FALSE, warning=FALSE,fig.align='left',echo = FALSE,message=FALSE,fig.width=8, fig.height=6}
turnout_mess_2011 <-ggplot(data_RUregions, aes(x = per_violmess_all_parl11, y = log(turnout_gd2011))) +
  geom_point(aes(label =  r_name),colour = "indianred2", size = 3) + theme_minimal() +  labs(y = "Turnout %", x = "% messages on electoral violations in State Duma elections 2011") + geom_smooth(method="loess") 
#turnout_mess_2011

ggplotly(turnout_mess_2011)
```

### Presidential elections 2012
```{r, error=FALSE, warning=FALSE,fig.align='left',echo = FALSE,message=FALSE,fig.width=8, fig.height=6}
turnout_mess_2012 <-ggplot(data_RUregions, aes(x = per_violmess_all_pres12, y = log(turnout_presd_2012))) +
  geom_point(aes(label =  r_name),colour = "indianred2", size = 3) + theme_minimal() +  labs(y = "Turnout %", x = "% messages on electoral violations in Presidential elections 2012") + geom_smooth(method="loess") 
#turnout_mess_2012
ggplotly(turnout_mess_2012)
```


### State Duma elections 2016
```{r, error=FALSE, warning=FALSE,fig.align='left',echo = FALSE,message=FALSE,fig.width=8, fig.height=6}
turnout_mess_2016 <-ggplot(data_RUregions, aes(x = per_violmess_all_parl16, y = log(turnout_gd2016))) +
  geom_point(aes(label =  r_name),colour = "indianred2", size = 3) + theme_minimal() +  labs(y = "Turnout %", x = "% messages on electoral violations in State Duma elections 2016") + geom_smooth(method="loess") 
#turnout_mess_2016

turnout_mess_2016_plotly<- ggplotly(turnout_mess_2016)
turnout_mess_2016_plotly
```



### Presidential elections 2018
```{r, error=FALSE, warning=FALSE,fig.align='left',echo = FALSE,message=FALSE,fig.width=8, fig.height=6}
turnout_mess_2018 <-ggplot(data_RUregions, aes(x = per_violmess_all_pres18, y = log(turnout_presd_2018))) +
  geom_point(aes(label =  r_name),colour = "indianred2", size = 3) + theme_minimal() +  labs(y = "Turnout %", x = "% messages on electoral violations in Presidential elections 2018") + geom_smooth(method="loess") 
#turnout_mess_2018

ggplotly(turnout_mess_2018)
```


### State Duma elections 2021
```{r, error=FALSE, warning=FALSE,fig.align='left',echo = FALSE,message=FALSE,fig.width=8, fig.height=6}

data_RUregions$turnout_gd2021 <- as.numeric(data_RUregions$turnout_gd2021)

turnout_mess_2021 <-ggplot(data_RUregions, aes(x = per_violmess_all_parl21, y = log(turnout_gd2021))) +
  geom_point(aes(label = r_name),colour = "indianred2", size = 2) + theme_minimal() +  
  labs(y = "Turnout %", x = "% messages on electoral violations in State Duma elections 2021") +
  geom_smooth(method='loess') 
#turnout_mess_2021

ggplotly(turnout_mess_2021)

#Sys.setenv("plotly_username"=  "valeria_caras")
#Sys.setenv("plotly_api_key"=  "5RQXXYgmgwxRPPcCwr2M")
#api_create(turnout_mess_2021, filename ="turnout_mess_2021")
```

## {-}

## Turnout and messaged on electoral fraud  for the State Duma elections 2021 with labels of regions
```{r,error=FALSE, warning=FALSE,fig.align='left',echo = FALSE,message=FALSE,fig.width=20, fig.height=12}

data_RUregions$turnout_gd2021 <- as.numeric(data_RUregions$turnout_gd2021)
turnout_mess_2021 <-ggplot(data_RUregions, aes(x = per_violmess_all_parl21, y = log(turnout_gd2021))) +
  geom_point(colour = "indianred2", size = 2) + theme_minimal() +  
  labs(y = "Turnout %", x = "% messages on electoral violations in State Duma elections 2021") +
  geom_smooth(method = "lm") + geom_label_repel(aes(label = data_RUregions$r_abbr), size = 3) +
  theme(axis.title.x = element_text(size = 18), axis.title.y = element_text(size = 18)) +
  scale_fill_discrete(labels=data_RUregions$r_abbr)
turnout_mess_2021

```

## Voting for the United Russia in State Duma elections 2021 and share of messages on electoral fraud
```{r, error=FALSE, warning=FALSE,fig.align='left',echo = FALSE,message=FALSE,fig.width=8, fig.height=6}
data_RUregions  <- data_RUregions %>% mutate(ur_voting_2021_log  = log(ur_voting_2021))

ur_fraud2021 <-ggplot(data_RUregions, aes(x = per_violmess_all_parl21, y = ur_voting_2021_log)) +
  geom_point(aes(label =  r_name),colour = "indianred2", size = 3) + theme_minimal() +  labs(y = "United Russia voting %", x = "% messages on electoral violations in State Duma elections 2021") + geom_smooth(method="loess") 
#turnout_mess_2018

ggplotly(ur_fraud2021)

#Sys.setenv("plotly_username"=  "valeria_caras")
#Sys.setenv("plotly_api_key"=  "5RQXXYgmgwxRPPcCwr2M")
#api_create(ur_fraud2021, filename ="grp_elections2021")

ur_fraud2021_filt <-data_RUregions %>% filter(r_name!= "Bryanskaya oblast'" & r_name!= "Ivanovskaya oblast'") %>%
ggplot(., aes(x = per_violmess_all_parl21, y = ur_voting_2021_log)) +
  geom_point(aes(label =  r_name),colour = "indianred2", size = 3) + theme_minimal() +  labs(y = "United Russia voting %", x = "% messages on electoral violations in State Duma elections 2021") + geom_smooth(method="loess") +
  scale_y_continuous(labels = c(20,40,60,80))

ggplotly(ur_fraud2021_filt)
Sys.setenv("plotly_username"=  "valeria_caras")
Sys.setenv("plotly_api_key"=  "5RQXXYgmgwxRPPcCwr2M")
api_create(ur_fraud2021_filt, filename ="ur_fraud2021_filt")
```



```{r,error=FALSE, warning=FALSE,fig.align='left',echo = FALSE,message=FALSE,fig.width=20, fig.height=12}
ur_fraud2021_static <-ggplot(data_RUregions, aes(x = per_violmess_all_parl21, y = log(ur_voting_2021))) +
  geom_point(colour = "indianred2", size = 2) + theme_minimal() +  
  labs(y = "United Russia voting %", x = "% messages on electoral violations in State Duma elections 2021") +
  geom_smooth(method = "lm") + geom_label_repel(aes(label = data_RUregions$r_abbr), size = 3) +
  theme(axis.title.x = element_text(size = 18), axis.title.y = element_text(size = 18)) +
  scale_fill_discrete(labels=data_RUregions$r_abbr)
ur_fraud2021_static
```

## Voting for the Communist Party of the Russian Federation in State Duma elections 2021 and share of messages on electoral fraud
```{r, error=FALSE, warning=FALSE,fig.align='left',echo = FALSE,message=FALSE,fig.width=8, fig.height=6}
cprf_fraud2021 <-ggplot(data_RUregions, aes(x = per_violmess_all_parl21, y = log(kprf_voting_2021))) +
  geom_point(aes(label =  r_name),colour = "indianred2", size = 3) + theme_minimal() +  labs(y = "CPRF voting %", x = "% messages on electoral violations in State Duma elections 2021") + geom_smooth(method="loess") 
#turnout_mess_2018

ggplotly(cprf_fraud2021)

#Sys.setenv("plotly_username"=  "valeria_caras")
#Sys.setenv("plotly_api_key"=  "5RQXXYgmgwxRPPcCwr2M")
#api_create(cprf_fraud2021, filename ="cprf_fraud2021")

cprf_fraud2021_filt <-data_RUregions %>% filter(r_name!= "Bryanskaya oblast'" & r_name!= "Ivanovskaya oblast'") %>%
ggplot(., aes(x = per_violmess_all_parl21, y = log(kprf_voting_2021))) +
  geom_point(aes(label =  r_name),colour = "indianred2", size = 3) + theme_minimal() +  labs(y = "CPRF Russia voting %", x = "% messages on electoral violations in State Duma elections 2021") + geom_smooth(method="loess") 

ggplotly(cprf_fraud2021_filt)
Sys.setenv("plotly_username"=  "valeria_caras")
Sys.setenv("plotly_api_key"=  "5RQXXYgmgwxRPPcCwr2M")
api_create(cprf_fraud2021_filt, filename ="cprf_fraud2021_filt")
```

```{r,error=FALSE, warning=FALSE,fig.align='left',echo = FALSE,message=FALSE,fig.width=20, fig.height=12}
cprf_fraud2021_static <-ggplot(data_RUregions, aes(x = per_violmess_all_parl21, y = log(kprf_voting_2021))) +
  geom_point(colour = "indianred2", size = 2) + theme_minimal() +  
  labs(y = "CPRF voting voting %", x = "% messages on electoral violations in State Duma elections 2021") +
  geom_smooth(method = "lm") + geom_label_repel(aes(label = data_RUregions$r_abbr), size = 3) +
  theme(axis.title.x = element_text(size = 18), axis.title.y = element_text(size = 18)) +
  scale_fill_discrete(labels=data_RUregions$r_abbr)
cprf_fraud2021_static
```


